---
title: "Introduction to R"
subtitle: "<br/> Day 1: Introduction"
author: "Sebastian Barfort"
date: "Jan. 2017"
output:
  xaringan::moon_reader:
    css: example.css
    seal: no
    nature:
      highlightStyle: arta
      ratio: '16:9'
---

```{r setup, include=FALSE}
options(htmltools.dir.version = FALSE)
```

# 

[**Introduction to R**](www.sebastianbarfort.github.io/intro_r_phd/) <br>
Sebastian Barfort 

PhD Course <br>
Department of Political Science <br>
University of Copenhagen 

---

# 

**Postdoctoral Researcher**, <br> London School of Economics. <br>
2015: PhD, Economics, <br> University of Copenhagen 

2015-16: Co-taught [Social Data Science](https://sebastianbarfort.github.io/sds_summer/)  with <br> David Dreyer Lassen.


---

class: center

# 

[**Stack**](www.stack.com) is a presentation library <br>
with simple, scroll-based navigation.

<br>
<p class = "grey"> bla bla bla.  

---

<br>

<p>In addition to the mouse,
    <br>you can scroll with the keyboard:
    <br>use the <b>arrow keys</b>,
    <br>the <b>space bar</b>,
    <br>or <b>page up</b> and <b>page down</b>.

<br>
<p class="grey">Multiple key presses will skip multiple slides.

---

class: center

# 

<font color="grey">Topic 1</font> Bla bla bla. 

---

# Thanks!

Slides **created** via the R package [**xaringan**](https://github.com/yihui/xaringan).

Slides created via the **R package** [**xaringan**](https://github.com/yihui/xaringan).

Slides created via the R package [**xaringan**](https://github.com/yihui/xaringan).

The chakra comes from [remark.js](https://remarkjs.com), [**knitr**](http://yihui.name/knitr), and [R Markdown](https://rmarkdown.rstudio.com).

---

# 

Bla bla bla 

More Blac bla blab lab 

Some bullet points:

- Bla bla bla
- Bla xxx bla bla 
- Even more bla bla 

---

```{r comment='#', message = FALSE}
library("dplyr")
fit = lm(dist ~ 1 + speed, data = cars)
coef(summary(fit))
dojutsu = c('地爆天星', '天照', '加具土命', '神威', '須佐能乎', '無限月読')
grep('天', dojutsu, value = TRUE)
```

---

# R plots

```{r cars, fig.height=4, dev='svg'}
par(mar = c(4, 4, 1, .1))
plot(cars, pch = 19, col = 'darkgray', las = 1)
abline(fit, lwd = 2)
```

---

# R plots

```{r, echo = FALSE, fig.height=4, dev='svg'}
par(mar = c(4, 4, 1, .1))
plot(cars, pch = 19, col = 'darkgray', las = 1)
abline(fit, lwd = 2)
```

---

class: center

# Hand seals (印)

Press `h` or `?` to see the possible ninjutsu you can use.

![](https://upload.wikimedia.org/wikipedia/commons/7/7e/Mudra-Naruto-KageBunshin.svg)

---

class: center, middle

# Thanks!

Slides **created** via the R package [**xaringan**](https://github.com/yihui/xaringan).

Slides created via the **R package** [**xaringan**](https://github.com/yihui/xaringan).

Slides created via the R package [**xaringan**](https://github.com/yihui/xaringan).

The chakra comes from [remark.js](https://remarkjs.com), [**knitr**](http://yihui.name/knitr), and [R Markdown](https://rmarkdown.rstudio.com).
